Evaluating Model Performances

### 2019-04-08 Scripts/evaluating_model_performances.Rmd
editted results script

all_rfperfs_gm12878$Performance <- c(round(rfperf_gm12878_10kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_ROS_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_10kb_SMOTE_dist[17,2],2), #auc

                                     round(rfperf_gm12878_25kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_ROS_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_25kb_SMOTE_dist[17,2],2), #auc

                                     round(rfperf_gm12878_50kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_ROS_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_50kb_SMOTE_dist[17,2],2), #auc

                                     round(rfperf_gm12878_100kb_none_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_none_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_none_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_ROS_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_RUS_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_gm12878_100kb_SMOTE_dist[17,2],2), #auc

                                     round(rfperf_gm12878_10kb_none_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_none_op[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_none_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_ROS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_ROS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_ROS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_RUS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_RUS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_RUS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_SMOTE_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_SMOTE_op[19,2],2), #auprc
                                          round(rfperf_gm12878_10kb_SMOTE_dist[19,2],2), #auprc

                                     round(rfperf_gm12878_25kb_none_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_none_op[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_none_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_ROS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_ROS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_ROS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_RUS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_RUS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_RUS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_SMOTE_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_SMOTE_op[19,2],2), #auprc
                                          round(rfperf_gm12878_25kb_SMOTE_dist[19,2],2), #auprc

                                     round(rfperf_gm12878_50kb_none_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_none_op[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_none_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_ROS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_ROS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_ROS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_RUS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_RUS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_RUS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_SMOTE_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_SMOTE_op[19,2],2), #auprc
                                          round(rfperf_gm12878_50kb_SMOTE_dist[19,2],2), #auprc

                                     round(rfperf_gm12878_100kb_none_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_none_op[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_none_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_ROS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_ROS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_ROS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_RUS_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_RUS_op[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_RUS_dist[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_SMOTE_oc[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_SMOTE_op[19,2],2), #auprc
                                          round(rfperf_gm12878_100kb_SMOTE_dist[19,2],2), #auprc

                                     round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_ROS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_ROS_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_ROS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_10kb_SMOTE_dist[16,2],2), #f1

                                     round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_ROS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_ROS_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_ROS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_25kb_SMOTE_dist[16,2],2), #f1

                                     round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_ROS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_ROS_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_ROS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_50kb_SMOTE_dist[16,2],2), #f1

                                     round(rfperf_gm12878_100kb_none_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_none_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_none_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_ROS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_ROS_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_ROS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_RUS_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_RUS_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_RUS_dist[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_SMOTE_oc[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_SMOTE_op[16,2],2), #f1
                                          round(rfperf_gm12878_100kb_SMOTE_dist[16,2],2), #f1

                                     round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_ROS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_ROS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_ROS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_10kb_SMOTE_dist[15,2],2), #mcc

                                     round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_ROS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_ROS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_ROS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_25kb_SMOTE_dist[15,2],2), #mcc

                                     round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_ROS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_ROS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_ROS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_50kb_SMOTE_dist[15,2],2), #mcc

                                     round(rfperf_gm12878_100kb_none_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_none_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_none_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_ROS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_ROS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_ROS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_RUS_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_RUS_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_RUS_dist[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_SMOTE_oc[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_SMOTE_op[15,2],2), #mcc
                                          round(rfperf_gm12878_100kb_SMOTE_dist[15,2],2) #mcc
)

@@

all_rfperfs_K562$Performance <- c(round(rfperf_K562_10kb_none_oc[17,2],2), #auc
                                          round(rfperf_K562_10kb_none_op[17,2],2), #auc
                                          round(rfperf_K562_10kb_none_dist[17,2],2), #auc
                                          round(rfperf_K562_10kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_K562_10kb_ROS_op[17,2],2), #auc
                                          round(rfperf_K562_10kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_K562_10kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_K562_10kb_RUS_op[17,2],2), #auc
                                          round(rfperf_K562_10kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_K562_10kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_K562_10kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_K562_10kb_SMOTE_dist[17,2],2), #auc

                                     round(rfperf_K562_25kb_none_oc[17,2],2), #auc
                                          round(rfperf_K562_25kb_none_op[17,2],2), #auc
                                          round(rfperf_K562_25kb_none_dist[17,2],2), #auc
                                          round(rfperf_K562_25kb_ROS_oc[17,2],2), #auc
                                          round(rfperf_K562_25kb_ROS_op[17,2],2), #auc
                                          round(rfperf_K562_25kb_ROS_dist[17,2],2), #auc
                                          round(rfperf_K562_25kb_RUS_oc[17,2],2), #auc
                                          round(rfperf_K562_25kb_RUS_op[17,2],2), #auc
                                          round(rfperf_K562_25kb_RUS_dist[17,2],2), #auc
                                          round(rfperf_K562_25kb_SMOTE_oc[17,2],2), #auc
                                          round(rfperf_K562_25kb_SMOTE_op[17,2],2), #auc
                                          round(rfperf_K562_25kb_SMOTE_dist[17,2],2), #auc

>>>>

all_rfperfs_gm12878$Performance <- c(rfperf_gm12878_10kb_none_oc[17,2], #auc
                                          rfperf_gm12878_10kb_none_op[17,2], #auc
                                          rfperf_gm12878_10kb_none_dist[17,2], #auc
                                          rfperf_gm12878_10kb_ROS_oc[17,2], #auc
                                          rfperf_gm12878_10kb_ROS_op[17,2], #auc
                                          rfperf_gm12878_10kb_ROS_dist[17,2], #auc
                                          rfperf_gm12878_10kb_RUS_oc[17,2], #auc
                                          rfperf_gm12878_10kb_RUS_op[17,2], #auc
                                          rfperf_gm12878_10kb_RUS_dist[17,2], #auc
                                          rfperf_gm12878_10kb_SMOTE_oc[17,2], #auc
                                          rfperf_gm12878_10kb_SMOTE_op[17,2], #auc
                                          rfperf_gm12878_10kb_SMOTE_dist[17,2], #auc

                                     rfperf_gm12878_25kb_none_oc[17,2], #auc
                                          rfperf_gm12878_25kb_none_op[17,2], #auc
                                          rfperf_gm12878_25kb_none_dist[17,2], #auc
                                          rfperf_gm12878_25kb_ROS_oc[17,2], #auc
                                          rfperf_gm12878_25kb_ROS_op[17,2], #auc
                                          rfperf_gm12878_25kb_ROS_dist[17,2], #auc
                                          rfperf_gm12878_25kb_RUS_oc[17,2], #auc
                                          rfperf_gm12878_25kb_RUS_op[17,2], #auc
                                          rfperf_gm12878_25kb_RUS_dist[17,2], #auc
                                          rfperf_gm12878_25kb_SMOTE_oc[17,2], #auc
                                          rfperf_gm12878_25kb_SMOTE_op[17,2], #auc
                                          rfperf_gm12878_25kb_SMOTE_dist[17,2], #auc

                                     rfperf_gm12878_50kb_none_oc[17,2], #auc
                                          rfperf_gm12878_50kb_none_op[17,2], #auc
                                          rfperf_gm12878_50kb_none_dist[17,2], #auc
                                          rfperf_gm12878_50kb_ROS_oc[17,2], #auc
                                          rfperf_gm12878_50kb_ROS_op[17,2], #auc
                                          rfperf_gm12878_50kb_ROS_dist[17,2], #auc
                                          rfperf_gm12878_50kb_RUS_oc[17,2], #auc
                                          rfperf_gm12878_50kb_RUS_op[17,2], #auc
                                          rfperf_gm12878_50kb_RUS_dist[17,2], #auc
                                          rfperf_gm12878_50kb_SMOTE_oc[17,2], #auc
                                          rfperf_gm12878_50kb_SMOTE_op[17,2], #auc
                                          rfperf_gm12878_50kb_SMOTE_dist[17,2], #auc

                                     rfperf_gm12878_100kb_none_oc[17,2], #auc
                                          rfperf_gm12878_100kb_none_op[17,2], #auc
                                          rfperf_gm12878_100kb_none_dist[17,2], #auc
                                          rfperf_gm12878_100kb_ROS_oc[17,2], #auc
                                          rfperf_gm12878_100kb_ROS_op[17,2], #auc
                                          rfperf_gm12878_100kb_ROS_dist[17,2], #auc
                                          rfperf_gm12878_100kb_RUS_oc[17,2], #auc
                                          rfperf_gm12878_100kb_RUS_op[17,2], #auc
                                          rfperf_gm12878_100kb_RUS_dist[17,2], #auc
                                          rfperf_gm12878_100kb_SMOTE_oc[17,2], #auc
                                          rfperf_gm12878_100kb_SMOTE_op[17,2], #auc
                                          rfperf_gm12878_100kb_SMOTE_dist[17,2], #auc

                                     rfperf_gm12878_10kb_none_oc[19,2], #auprc
                                          rfperf_gm12878_10kb_none_op[19,2], #auprc
                                          rfperf_gm12878_10kb_none_dist[19,2], #auprc
                                          rfperf_gm12878_10kb_ROS_oc[19,2], #auprc
                                          rfperf_gm12878_10kb_ROS_op[19,2], #auprc
                                          rfperf_gm12878_10kb_ROS_dist[19,2], #auprc
                                          rfperf_gm12878_10kb_RUS_oc[19,2], #auprc
                                          rfperf_gm12878_10kb_RUS_op[19,2], #auprc
                                          rfperf_gm12878_10kb_RUS_dist[19,2], #auprc
                                          rfperf_gm12878_10kb_SMOTE_oc[19,2], #auprc
                                          rfperf_gm12878_10kb_SMOTE_op[19,2], #auprc
                                          rfperf_gm12878_10kb_SMOTE_dist[19,2], #auprc

                                     rfperf_gm12878_25kb_none_oc[19,2], #auprc
                                          rfperf_gm12878_25kb_none_op[19,2], #auprc
                                          rfperf_gm12878_25kb_none_dist[19,2], #auprc
                                          rfperf_gm12878_25kb_ROS_oc[19,2], #auprc
                                          rfperf_gm12878_25kb_ROS_op[19,2], #auprc
                                          rfperf_gm12878_25kb_ROS_dist[19,2], #auprc
                                          rfperf_gm12878_25kb_RUS_oc[19,2], #auprc
                                          rfperf_gm12878_25kb_RUS_op[19,2], #auprc
                                          rfperf_gm12878_25kb_RUS_dist[19,2], #auprc
                                          rfperf_gm12878_25kb_SMOTE_oc[19,2], #auprc
                                          rfperf_gm12878_25kb_SMOTE_op[19,2], #auprc
                                          rfperf_gm12878_25kb_SMOTE_dist[19,2], #auprc

                                     rfperf_gm12878_50kb_none_oc[19,2], #auprc
                                          rfperf_gm12878_50kb_none_op[19,2], #auprc
                                          rfperf_gm12878_50kb_none_dist[19,2], #auprc
                                          rfperf_gm12878_50kb_ROS_oc[19,2], #auprc
                                          rfperf_gm12878_50kb_ROS_op[19,2], #auprc
                                          rfperf_gm12878_50kb_ROS_dist[19,2], #auprc
                                          rfperf_gm12878_50kb_RUS_oc[19,2], #auprc
                                          rfperf_gm12878_50kb_RUS_op[19,2], #auprc
                                          rfperf_gm12878_50kb_RUS_dist[19,2], #auprc
                                          rfperf_gm12878_50kb_SMOTE_oc[19,2], #auprc
                                          rfperf_gm12878_50kb_SMOTE_op[19,2], #auprc
                                          rfperf_gm12878_50kb_SMOTE_dist[19,2], #auprc

                                     rfperf_gm12878_100kb_none_oc[19,2], #auprc
                                          rfperf_gm12878_100kb_none_op[19,2], #auprc
                                          rfperf_gm12878_100kb_none_dist[19,2], #auprc
                                          rfperf_gm12878_100kb_ROS_oc[19,2], #auprc
                                          rfperf_gm12878_100kb_ROS_op[19,2], #auprc
                                          rfperf_gm12878_100kb_ROS_dist[19,2], #auprc
                                          rfperf_gm12878_100kb_RUS_oc[19,2], #auprc
                                          rfperf_gm12878_100kb_RUS_op[19,2], #auprc
                                          rfperf_gm12878_100kb_RUS_dist[19,2], #auprc
                                          rfperf_gm12878_100kb_SMOTE_oc[19,2], #auprc
                                          rfperf_gm12878_100kb_SMOTE_op[19,2], #auprc
                                          rfperf_gm12878_100kb_SMOTE_dist[19,2], #auprc

                                     rfperf_gm12878_10kb_none_oc[16,2], #f1
                                          rfperf_gm12878_10kb_none_op[16,2], #f1
                                          rfperf_gm12878_10kb_none_dist[16,2], #f1
                                          rfperf_gm12878_10kb_ROS_oc[16,2], #f1
                                          rfperf_gm12878_10kb_ROS_op[16,2], #f1
                                          rfperf_gm12878_10kb_ROS_dist[16,2], #f1
                                          rfperf_gm12878_10kb_RUS_oc[16,2], #f1
                                          rfperf_gm12878_10kb_RUS_op[16,2], #f1
                                          rfperf_gm12878_10kb_RUS_dist[16,2], #f1
                                          rfperf_gm12878_10kb_SMOTE_oc[16,2], #f1
                                          rfperf_gm12878_10kb_SMOTE_op[16,2], #f1
                                          rfperf_gm12878_10kb_SMOTE_dist[16,2], #f1

                                     rfperf_gm12878_25kb_none_oc[16,2], #f1
                                          rfperf_gm12878_25kb_none_op[16,2], #f1
                                          rfperf_gm12878_25kb_none_dist[16,2], #f1
                                          rfperf_gm12878_25kb_ROS_oc[16,2], #f1
                                          rfperf_gm12878_25kb_ROS_op[16,2], #f1
                                          rfperf_gm12878_25kb_ROS_dist[16,2], #f1
                                          rfperf_gm12878_25kb_RUS_oc[16,2], #f1
                                          rfperf_gm12878_25kb_RUS_op[16,2], #f1
                                          rfperf_gm12878_25kb_RUS_dist[16,2], #f1
                                          rfperf_gm12878_25kb_SMOTE_oc[16,2], #f1
                                          rfperf_gm12878_25kb_SMOTE_op[16,2], #f1
                                          rfperf_gm12878_25kb_SMOTE_dist[16,2], #f1

                                     rfperf_gm12878_50kb_none_oc[16,2], #f1
                                          rfperf_gm12878_50kb_none_op[16,2], #f1
                                          rfperf_gm12878_50kb_none_dist[16,2], #f1
                                          rfperf_gm12878_50kb_ROS_oc[16,2], #f1
                                          rfperf_gm12878_50kb_ROS_op[16,2], #f1
                                          rfperf_gm12878_50kb_ROS_dist[16,2], #f1
                                          rfperf_gm12878_50kb_RUS_oc[16,2], #f1
                                          rfperf_gm12878_50kb_RUS_op[16,2], #f1
                                          rfperf_gm12878_50kb_RUS_dist[16,2], #f1
                                          rfperf_gm12878_50kb_SMOTE_oc[16,2], #f1
                                          rfperf_gm12878_50kb_SMOTE_op[16,2], #f1
                                          rfperf_gm12878_50kb_SMOTE_dist[16,2], #f1

                                     rfperf_gm12878_100kb_none_oc[16,2], #f1
                                          rfperf_gm12878_100kb_none_op[16,2], #f1
                                          rfperf_gm12878_100kb_none_dist[16,2], #f1
                                          rfperf_gm12878_100kb_ROS_oc[16,2], #f1
                                          rfperf_gm12878_100kb_ROS_op[16,2], #f1
                                          rfperf_gm12878_100kb_ROS_dist[16,2], #f1
                                          rfperf_gm12878_100kb_RUS_oc[16,2], #f1
                                          rfperf_gm12878_100kb_RUS_op[16,2], #f1
                                          rfperf_gm12878_100kb_RUS_dist[16,2], #f1
                                          rfperf_gm12878_100kb_SMOTE_oc[16,2], #f1
                                          rfperf_gm12878_100kb_SMOTE_op[16,2], #f1
                                          rfperf_gm12878_100kb_SMOTE_dist[16,2], #f1

                                     rfperf_gm12878_10kb_none_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_none_op[15,2], #mcc
                                          rfperf_gm12878_10kb_none_dist[15,2], #mcc
                                          rfperf_gm12878_10kb_ROS_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_ROS_op[15,2], #mcc
                                          rfperf_gm12878_10kb_ROS_dist[15,2], #mcc
                                          rfperf_gm12878_10kb_RUS_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_RUS_op[15,2], #mcc
                                          rfperf_gm12878_10kb_RUS_dist[15,2], #mcc
                                          rfperf_gm12878_10kb_SMOTE_oc[15,2], #mcc
                                          rfperf_gm12878_10kb_SMOTE_op[15,2], #mcc
                                          rfperf_gm12878_10kb_SMOTE_dist[15,2], #mcc

                                     rfperf_gm12878_25kb_none_oc[15,2], #mcc
                                          rfperf_gm12878_25kb_none_op[15,2], #mcc
                                          rfperf_gm12878_25kb_none_dist[15,2], #mcc
                                          rfperf_gm12878_25kb_ROS_oc[15,2], #mcc
                                          rfperf_gm12878_25kb_ROS_op[15,2], #mcc
                                          rfperf_gm12878_25kb_ROS_dist[15,2], #mcc
                                          rfperf_gm12878_25kb_RUS_oc[15,2], #mcc
                                          rfperf_gm12878_25kb_RUS_op[15,2], #mcc
                                          rfperf_gm12878_25kb_RUS_dist[15,2], #mcc
                                          rfperf_gm12878_25kb_SMOTE_oc[15,2], #mcc
                                          rfperf_gm12878_25kb_SMOTE_op[15,2], #mcc
                                          rfperf_gm12878_25kb_SMOTE_dist[15,2], #mcc

                                     rfperf_gm12878_50kb_none_oc[15,2], #mcc
                                          rfperf_gm12878_50kb_none_op[15,2], #mcc
                                          rfperf_gm12878_50kb_none_dist[15,2], #mcc
                                          rfperf_gm12878_50kb_ROS_oc[15,2], #mcc
                                          rfperf_gm12878_50kb_ROS_op[15,2], #mcc
                                          rfperf_gm12878_50kb_ROS_dist[15,2], #mcc
                                          rfperf_gm12878_50kb_RUS_oc[15,2], #mcc
                                          rfperf_gm12878_50kb_RUS_op[15,2], #mcc
                                          rfperf_gm12878_50kb_RUS_dist[15,2], #mcc
                                          rfperf_gm12878_50kb_SMOTE_oc[15,2], #mcc
                                          rfperf_gm12878_50kb_SMOTE_op[15,2], #mcc
                                          rfperf_gm12878_50kb_SMOTE_dist[15,2], #mcc

                                     rfperf_gm12878_100kb_none_oc[15,2], #mcc
                                          rfperf_gm12878_100kb_none_op[15,2], #mcc
                                          rfperf_gm12878_100kb_none_dist[15,2], #mcc
                                          rfperf_gm12878_100kb_ROS_oc[15,2], #mcc
                                          rfperf_gm12878_100kb_ROS_op[15,2], #mcc
                                          rfperf_gm12878_100kb_ROS_dist[15,2], #mcc
                                          rfperf_gm12878_100kb_RUS_oc[15,2], #mcc
                                          rfperf_gm12878_100kb_RUS_op[15,2], #mcc
                                          rfperf_gm12878_100kb_RUS_dist[15,2], #mcc
                                          rfperf_gm12878_100kb_SMOTE_oc[15,2], #mcc
                                          rfperf_gm12878_100kb_SMOTE_op[15,2], #mcc
                                          rfperf_gm12878_100kb_SMOTE_dist[15,2] #mcc
)

@@

all_rfperfs_K562$Performance <- c(rfperf_K562_10kb_none_oc[17,2], #auc
                                          rfperf_K562_10kb_none_op[17,2], #auc
                                          rfperf_K562_10kb_none_dist[17,2], #auc
                                          rfperf_K562_10kb_ROS_oc[17,2], #auc
                                          rfperf_K562_10kb_ROS_op[17,2], #auc
                                          rfperf_K562_10kb_ROS_dist[17,2], #auc
                                          rfperf_K562_10kb_RUS_oc[17,2], #auc
                                          rfperf_K562_10kb_RUS_op[17,2], #auc
                                          rfperf_K562_10kb_RUS_dist[17,2], #auc
                                          rfperf_K562_10kb_SMOTE_oc[17,2], #auc
                                          rfperf_K562_10kb_SMOTE_op[17,2], #auc
                                          rfperf_K562_10kb_SMOTE_dist[17,2], #auc

                                     rfperf_K562_25kb_none_oc[17,2], #auc
                                          rfperf_K562_25kb_none_op[17,2], #auc
                                          rfperf_K562_25kb_none_dist[17,2], #auc
                                          rfperf_K562_25kb_ROS_oc[17,2], #auc
                                          rfperf_K562_25kb_ROS_op[17,2], #auc
                                          rfperf_K562_25kb_ROS_dist[17,2], #auc
                                          rfperf_K562_25kb_RUS_oc[17,2], #auc
                                          rfperf_K562_25kb_RUS_op[17,2], #auc
                                          rfperf_K562_25kb_RUS_dist[17,2], #auc
                                          rfperf_K562_25kb_SMOTE_oc[17,2], #auc
                                          rfperf_K562_25kb_SMOTE_op[17,2], #auc
                                          rfperf_K562_25kb_SMOTE_dist[17,2], #auc
